\documentclass[10pt,conference,compsocconf]{IEEEtran}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{balance}
\usepackage{blindtext}
\usepackage{comment}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{pifont}
\usepackage[justification=centering]{caption} %% for centering the caption
\usepackage[belowskip=-5pt,aboveskip=10pt]{caption} %for the blank above and below caption
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}


\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Tentative: Improving big data processing at large scale on supercomputers using multithreading and advanced MPI features }


% author names and affiliations
% use a multiple column layout for up to three different
% affiliations


\author{ \IEEEauthorblockN{Boyu Zhang\IEEEauthorrefmark{1}, Wesley 
    Bland\IEEEauthorrefmark{2}, Pavan Balaji\IEEEauthorrefmark{3},
    Michela Taufer\IEEEauthorrefmark{1}}
  \IEEEauthorblockA{\IEEEauthorrefmark{1}University of Delaware
    \\\{bzhang, taufer\}@udel.edu}
  \IEEEauthorblockA{\IEEEauthorrefmark{2}Intel Corporation
    \\wesley.bland@intel.com}
  \IEEEauthorblockA{\IEEEauthorrefmark{3}Argonne National Laboratory
     \\balaji@anl.gov} }

% make the title area
\maketitle

\begin{abstract}
%\boldmath
NA.
\end{abstract}

% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

% no keywords
% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\input{text/intro.tex}
\input{text/background.tex}
\input{text/method.tex}
\input{text/evaluation.tex}
\input{text/related_work.tex}
\input{text/conclusions.tex}

\balance


% use section* for acknowledgement
\section*{Acknowledgment}
This work is supported in part by NSF grants: DMS 0800272/0800266, and CCF-SHF 1318445/1318417. This work used the Extreme Science and Engineering Discovery Environment (XSEDE), which is supported by National Science Foundation grant number OCI-1053575. The authors want to thank Dr. Vijay Pande and T. J. Lane from Stanford  for providing us with the dataset for our tests. All the software will be made available before the conference. 

%\newpage
% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
%\begin{thebibliography}{11}
%
%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
%
%\end{thebibliography}

% Generated by tran.bst, version: 1.13 (2008/09/30)
%\small
\begin{thebibliography}{10}
%\providecommand{\url}[1]{#1}
%\csname url@samestyle\endcsname
%\providecommand{\newblock}{\relax}
%\providecommand{\bibinfo}[2]{#2}
%\providecommand{\BIBentrySTDinterwordspacing}{\spaceskip=0pt\relax}
%\providecommand{\BIBentryALTinterwordstretchfactor}{4}
%\providecommand{\BIBentryALTinterwordspacing}{\spaceskip=\fontdimen2\font plus
%\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
%  \fontdimen4\font\relax}
%\providecommand{\BIBforeignlanguage}[2]{{%
%\expandafter\ifx\csname l@#1\endcsname\relax
%\typeout{** WARNING: tran.bst: No hyphenation pattern has been}%
%\typeout{** loaded for the language `#1'. Using the pattern for}%
%\typeout{** the default language instead.}%
%\else
%\language=\csname l@#1\endcsname
%\fi
%#2}}
%\providecommand{\BIBdecl}{\relax}
%\BIBdecl

\bibitem{Phillips2011} J.~Phillips et al., ``Validating clustering of
  molecular dynamics simulations using polymer models,'' \emph{BMC
    Bioinformatics}, vol.~12, no.~1, pp. 445--467, 2011.  
\bibitem{Tu2008} T.~Tu et al., ``A scalable parallel framework for
  analyzing terascale molecular dynamics simulation trajectories,'' in
  \emph{Proc. of the 2008 ACM/IEEE International Conference for High
    Performance Computing, Networking, Storage and Analysis (SC'08)}, pp. 1--12, 2008.
\bibitem{Best2002} C.~Best and H.~C. Hege, ``Visualizing and
  identifying conformational ensembles in molecular dynamics
  trajectories,'' \emph{Computing in Science Engineering}, vol.~4,
  no.~3, pp. 68--75, 2002.
\bibitem{bigdataweb} M. Stonebraker. (2012, Sept. 21). What does big
  data mean [ONLINE]. Available:
  http://cacm.acm.org/blogs/blog-cacm/155468-what-does-big-data-mean/fulltext
\bibitem{Bennett2012} J.~C. Bennett et al., ``Combining in-situ and
  in-transit processing to enable extreme-scale scientific analysis,''
  in \emph{Proc. of the 2012 ACM/IEEE International Conference for
    High Performance Computing, Networking, Storage and Analysis
    (SC'12)}, pp. 1--9, 2012.
\bibitem{Lakshminarasimhan2013} S.~Lakshminarasimhan et al.,
  ``Scalable in-situ scientific data encoding for analytical query
  processing,'' in \emph{Proc. of the 22nd International Symposium on
    High-performance Parallel and Distributed Computing (HPDC '13)}, pp. 1--12, 2013.
\bibitem{Cordeiro2011} R.~L.~F. Cordeiro et al., ``Clustering very
  large multi-dimensional datasets with {MapReduce},'' in
  \emph{Proc. of the 17th ACM SIGKDD International Conference on
    Knowledge Discovery and Data Mining (KDD'11)}, pp. 690--698, 2011.
\bibitem{Liu2013} J.~Liu et al., ``Segmented analysis for reducing
  data movement,'' in \emph{Proc. of the IEEE International conference
    on Big Data (BigData'13)}, 2013.
\bibitem{Pande2007} D.~L. Ensign et al., ``Heterogeneity even at the
  speed limit of folding: large-scale molecular dynamics study of a
  fast-folding variant of the villin headpiece,'' \emph{Journal of
    Molecular Biology}, vol.  374, no.~3, pp. 806--816, 2007.
\bibitem{Borg2009} I.~Borg and P.~J.~F. Groenen, \emph{Modern
  multidimensional scaling: theory and applications}, Springer, 2005.
\bibitem{FCM} R.~L. Cannon et al., ``Efficient implementation of the
  fuzzy c-means clustering algorithms,'' \emph{IEEE Transactions on
    Pattern Analysis and Machine Intelligence}, vol.~8, no.~2,
  pp. 248--255, 1986. 
    \bibitem{Mooi2011} E.~Mooi and M.~Sarstedt, ``Chapter 9 -
      clustering analysis", in \emph{A Concise Guide to Market
        Research: The Process, Data, and Methods Using {IBM} {Spss}
        Statistics}, Springer, 2011.  
\bibitem{pearson} G.~W. Snedecor and W.~G. Cochran, ``The sample
  correlation coefficient {R}", in \emph{Statistical Methods}, 7th
  ed. Iowa State Press,1980.
  \bibitem{Moler1995} C.~Moler, ``Why there isn't parallel {MATLAB},''
    \emph{Mathworks Newsletter}, vol.~00, pp. 1--12, 1995.
\bibitem{Moler2013} C. Moler, ``Parallel {MATLAB}: {from hell no to
  you bet},'' \emph{Thirty Years of Parallel Computing at Argonne: A
  Symposium}, May 2013.
\end{thebibliography}

%[Total times in seconds across processes broken down into distinctive components: Map (M), Shuffle (S), Overhead (O), Reduce (R), and Total (T).]
%This is the appendix.


% that's all folks
\end{document}



% LocalWords:  priori
